---
title: "Comparison of success rates"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)

hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(x_a, subscript(X, A))
hook(x_b, subscript(X, B))
hook(p_a, subscript(P, A))
hook(p_b, subscript(P, B))
hook(pct_a, subscript(P, '%A'))
hook(pct_b, subscript(P, '%B'))
hook(p_pool, subscript(p, "pool"))

task <- "chisquare6"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package="mistakes"))

## DATA GENERATION
repeat
{
  pct_a <- as.integer(round(runif(1, min=40, max=70)))
  pct_b <- as.integer(round(runif(1, min=40, max=70)))
  if (pct_a == pct_b)
    next
  
  n_a <- n_b <- as.integer(round(runif(1, min=20, max=45)))
  n <- n_a + n_b
  x_a <- pct_a / 100 * n_a
  x_b <- pct_b / 100 * n_b

  if (x_a %% 1 != 0 || x_b %% 1 != 0)
    next


  Q <- quote(search(chisquare6, chisquare6(pct_a, pct_b, n), .S, .R, .P, .E))
  S <- findall(Q, options=list(preproc=as.rolog), env=environment())

  if(problems(S))
    next

  break
}

t <- prepare(task=task, S)
sol <- format_feedback(t$correct, t$explanations, t$praise, t$blame, t$extra)
```

Question
========
In a behavioral experiment, `r n` participants are randomly assigned in equal numbers to two experimental conditions. 
The observed success rate is `r pct_a`% in condition A and `r pct_b`%  in condition B. 
Determine the $\chi^2$-statistic for testing whether the success probabilities in the two conditions are equal.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========
The $\chi^2$-statistic is calculated by: `r t$solution`

```{r solutionlist, echo = FALSE, results = "asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: chisquare6
