---
title: "Comparison of success rates"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)

hook(p_a, subscript(p, A))
hook(p_b, subscript(p, B))
hook(p_pool, subscript(p, "pool"))
hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(x_a, subscript(X, A))
hook(x_b, subscript(X, B))
hook(n, N)
hook(p_pool, subscript(p, "pool"))

task <- "chisquare1"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package="mistakes"))

## DATA GENERATION
repeat
{
  n_a <- as.integer(round(runif(1, min=20, max=45)))
  n_b <- as.integer(round(runif(1, min=20, max=45)))

  if(n_a == n_b)
    next
  n <- n_a + n_b
  x_a <- as.integer(round(runif(1, min=5, max=n_a - 5)))
  x_b <- as.integer(round(runif(1, min=5, max=n_b - 5)))
  p_a <- x_a / n_a
  p_b <- x_b / n_b
  p_pool <- (x_a + x_b) / (n_a + n_b)
  z <- (p_a - p_b) /sqrt(p_pool * (1 - p_pool) * (1 / n_a + 1 / n_b))

  if(abs(z) < 0.5)
    next
  if(abs(z) > 3.0)
    next
  
  alpha <- 0.05
  Q <- quote(search(chisquare1, chisquare1(p_a, p_b, n_a, n_b, x_a, x_b), .S, .R, .P, .E))
  S <- findall(Q, options=list(preproc=as.rolog), env=environment())

  if(problems(S))
    next

  break
}

t <- prepare(task=task, S)
sol <- format_feedback(t$correct, t$explanations, t$praise, t$blame, t$extra)
```

Question
========

In a randomized controlled trial, `r n` patients are observed.

`r n_a` patients are randomized to therapy group A and `r n_b` patients
are randomized to control group B. In group A, `r x_a` treatment successes
are observed, whereas in group B, `r x_b` treatment successes are observed.

Determine the $\chi^2$-statistic for testing whether the success probabilities
in the two groups are equal.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========
The $\chi^2$-statistic is calculated by: `r t$solution`

```{r solutionlist, echo = FALSE, results = "asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: chisquare1
