---
title: "Comparison of success rates"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)

hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(x_a, subscript(X, A))
hook(x_b, subscript(X, B))

task <- "chisquare3"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package="mistakes"))

## DATA GENERATION
repeat
{
  n_a <- as.integer(round(runif(1, min=20, max=45)))
  n_b <- as.integer(round(runif(1, min=20, max=45)))

  if(n_a == n_b)
    next
  x_a <- as.integer(round(runif(1, min=5, max=n_a - 5)))
  x_b <- as.integer(round(runif(1, min=5, max=n_b - 5)))

  Q <- quote(search(chisquare3, chisquare3(n_a, n_b, x_a, x_b), .S, .R, .P, .E))
  S <- findall(Q, options=list(preproc=as.rolog), env=environment())

  if(problems(S))
    next

  break
}

t <- prepare(task=task, S)
sol <- format_feedback(t$correct, t$explanations, t$praise, t$blame, t$extra)
```

Question
========

In a randomized controlled trial, group A is composed of `r n_a` patients, with `r x_a` showing treatment success, 
and group B is composed of `r n_b` patients, with `r x_b` treatment successes.
Determine the pooled success probability, $p_{\mathrm{pool}}$.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========
The pooled success probability is calculated by: `r t$solution`

```{r solutionlist, echo = FALSE, results = "asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: chisquare3
