---
title: "Comparison of success rates"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)

hook(p_a, subscript(p, A))
hook(p_b, subscript(p, B))
hook(p_pool, subscript(p, "pool"))
hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(x_a, subscript(X, A))
hook(x_b, subscript(X, B))
hook(n, N)

## DATA GENERATION
repeat
{
  n_a <- as.integer(round(runif(1, min=20, max=45)))
  n_b <- as.integer(round(runif(1, min=20, max=45)))

  if(n_a == n_b)
    next
  n <- n_a + n_b
  x_a <- as.integer(round(runif(1, min=5, max=n_a - 5)))
  x_b <- as.integer(round(runif(1, min=5, max=n_b - 5)))
  p_a <- x_a / n_a
  p_b <- x_b / n_b
  p_pool <- (x_a + x_b) / (n_a + n_b)
  z <- (p_a - p_b) /sqrt(p_pool * (1 - p_pool) * (1 / n_a + 1 / n_b))
  chisq <- z^2

  #Wrong
  z_wrong_n <- (p_a - p_b) / sqrt(p_pool * (1 - p_pool) *(1 / n + 1 / n))
  chisq_wrong_n <- z_wrong_n^2

  if(abs(z) < 0.5)
    next
  if(abs(z) > 3.0)
    next

  # different MC alternatives after rounding 
  vals <- c(p_pool, z, -z, chisq, chisq_wrong_n)

  if(length(unique(round(vals, 2))) < 5)
    next
  alpha <- 0.05
  break
}

rolog::consult(system.file("rexams/chisquare1.pl", package="mistakes"))

Q <- quote(search(chisquare1, chisquare1(p_a, p_b, p_pool, n_a, n_b, n), .S, .R, .P, .E))
S <- findall(Q, options=list(preproc=as.rolog), env=environment())

alternatives <- character(length(S))
correct <- logical(length(S))
explanations <- character(length(S))
praise <- list(length(S))
blame <- list(length(S))
extra <- list(length(S))

if(length(S) == 0)
  stop("No solutions found.")

for(i in 1:length(S))
{
  Si <- S[[i]]$S
  Ri <- S[[i]]$R
  Pi <- S[[i]]$P
  Ei <- S[[i]]$E

  alternatives[i] <- sprintf("%.2f", Ri)
  correct[i] <- all(expert(Pi))
  explanations[i] <- sprintf("The result matches the following expression: %s\n", mathml(Si))
  praise[[i]] <- praise("chisquare1", Pi)
  blame[[i]] <- blame("chisquare1", Pi)
  extra[[i]] <- feedback("chisquare1", Ei)
}

# number of MC alternatives, reduce if needed, but make sure the correct
# alternative is in the set
A <- length(S)
o <- sample(1:A)

# Shuffle
alternatives <- alternatives[o]
correct <- correct[o]
explanations <- explanations[o]
praise <- praise[o]
blame <- blame[o]
extra <- extra[o]
S <- S[o]

sol <- format_feedback(correct, explanations, praise, blame, extra)
```

Question
========

In a randomized controlled trial, `r n` patients are observed.

`r n_a` patients are randomized to therapy group A and `r n_b` patients
are randomized to control group B. In group A, `r x_a` treatment successes
are observed, whereas in group B, `r x_b` treatment successes are observed.

Determine the $\chi^2$-statistic for testing whether the success probabilities
in the two groups are equal.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(alternatives, markup="markdown")