---
title: "Mann-Whitney Competing probability"
---


```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)

hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(u, U)
hook(cp, CP)

task <- "mannwhitney2"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package="mistakes"))

## DATA GENERATION
repeat
{
  n_a <- sample(12:25, 1)
  n_b <- sample(15:30, 1)
  pairs <- n_a * n_b
  u <- sample(2:(pairs - 2), 1)

  Q <- quote(search(mannwhitney2, mannwhitney2(u, n_a, n_b), .S, .R, .P, .E))

  S <- findall(Q, options = list(preproc = as.rolog), env = environment())

  if(problems(S))
    next
  break
}

t <- prepare(task=task, S)

sol <- format_feedback(t$correct, t$explanations, t$praise, t$blame, t$extra)
```

Question
========

In a Mann-Whitney comparison, Grohp A contains `r n_a` participants and Group B
`r n_b` participants. Group A wins `r u` of the pairwise comparisons.

What is the estimated competing probability?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========
The estimated competing probability is given by: `r t$solution`

```{r solutionlist, echo = FALSE, results = "asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: mannwhitney2

