---
title: "Mann-Whitney U test"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)


hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(a_i, subscript(A, i))
hook(b_j, subscript(B, j))
hook(u, U)

task <- "mannwhitney1"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package="mistakes"))

## DATA GENERATION
repeat
{
  n_a <- 5L
  n_b <- 6L

  x <- sample(10:99, n_a + n_b, replace=FALSE)

  a <- sort(x[1:n_a])
  b <- sort(x[(n_a + 1):(n_a + n_b)])

  a1 <- a[1]
  a2 <- a[2]
  a3 <- a[3]
  a4 <- a[4]
  a5 <- a[5]
  
  b1 <- b[1]
  b2 <- b[2]
  b3 <- b[3]
  b4 <- b[4]
  b5 <- b[5]
  b6 <- b[6]

  u <- sum(outer(a, b, ">"))
  u_b <- n_a * n_b - u # I report them here to avoid calculations in pl
  pairs <- n_a * n_b
  a_win <- sum(sapply(a, function(x) any(x > b)))

  if(u <= 2)
    next
  if(u >= n_a*n_b - 2)
    next

  Q <- quote(search(mannwhitney1, mannwhitney1(u, u_b, pairs, a_win),
                  .S, .R, .P, .E))

  S <- findall(Q, options=list(preproc=as.rolog), env=environment())

  if(problems(S))
    next

  break
}

t <- prepare(task=task, S)
sol <- format_feedback(t$correct, t$explanations, t$praise, t$blame, t$extra)
```

Question
========

Two independent groups have the following observations:

Group A: `r paste(a, collapse=", ")`and Group B: `r paste(b, collapse=", ")` .
There are no ties.

Determine the Mann-Whitney $U$-statistic for group A.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========
The Mann-Whitney $U$-statistic is calculated by: `r t$solution`

```{r solutionlist, echo = FALSE, results = "asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: mannwhitney1