---
title: "Mann-Whitney z approximation"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)
library(knitr)

hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(u, U)

task <- "mannwhitney4"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package = "mistakes"))

## DATA GENERATION
repeat
{
  n_a <- sample(20:40, 1)
  n_b <- sample(20:40, 1)

 u <- sample(seq.int(ceiling(0.25*n_a*n_b),
      floor(0.75*n_a*n_b)), 1)

  if(2 * u == n_a * n_b)
    next

  Q <- quote(search(mannwhitney4, mannwhitney4(u, n_a, n_b), .S, .R, .P, .E))

  S <- findall(Q, options = list(preproc = as.rolog), env = environment())

  if(problems(S))
    next

  break
}

t <- prepare(task = task, S)

sol <- format_feedback(t$correct, t$explanations, t$praise, t$blame, t$extra)
```

Question
========

In a Mann-Whitney comparison, group A contains `r n_a` participants
and group B contains `r n_b` participants. There are no ties.
Group A wins `r u` of the `r n_a * n_b` pairwise comparisons.

Using the normal approximation of the U-distribution, determine the corresponding z-statistic, without applying a continuity correction.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========
Under the null hypothesis:

$$
E(U)=\frac{N_A N_B}{2},
\qquad
\mathrm{Var}(U)=\frac{N_A N_B(N_A+N_B+1)}{12}.
$$

The z-statistic is calculated as:

$$
z=
\frac{U-N_A N_B/2}
{\sqrt{N_A N_B(N_A+N_B+1)/12}}.
$$

The result is: `r t$solution`

```{r solutionlist, echo = FALSE, results = "asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: mannwhitney4
