---
title: "Mann-Whitney critical region"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)
library(knitr)

hook(n_a, subscript(N, A))
hook(n_b, subscript(N, B))
hook(u, U)
hook(u_crit, subscript(U, crit))

critical <- function(lower, upper) {
  sprintf("U <= %s or U >= %s", lower, upper)
}

upper_only <- function(upper) {
  sprintf("U >= %s", upper)
}

task <- "mannwhitney3"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package = "mistakes"))

ucrit <- function(n_a, n_b, alpha = 0.05)
{
  u <- 0:(n_a * n_b)
  upper <- 1 - pwilcox(u - 1, n_a, n_b)
  min(u[upper <= alpha / 2])
}

## DATA GENERATION
repeat
{
  n_a <- sample(10:18, 1)
  n_b <- sample(12:20, 1)

  u_crit <- ucrit(n_a, n_b)
  u_lower <- n_a * n_b - u_crit

  na_values <- (n_a-2):(n_a+2) # for table
  nb_values <- (n_b-2):(n_b+2)

  crit_table <- outer(na_values, nb_values,
    Vectorize(function(a, b) ucrit(a, b)))

  rownames(crit_table) <- na_values
  colnames(crit_table) <- nb_values

  Q <- quote(search(mannwhitney3, mannwhitney3(u_lower, u_crit), .S, .R, .P, .E))

  S <- findall(Q, options = list(preproc = as.rolog), env = environment())

  if(problems(S))
    next

  break
}

t <- prepare(task = task, S)

sol <- format_feedback(t$correct, t$explanations, t$praise, t$blame, t$extra)
```

Question
========

In a Mann-Whitney test, group A contains `r n_a` participants and group B 
contains `r n_b` participants. The table below gives the upper critical values 
of the Mann-Whitney $U$-distribution for a two-sided test at the 5% significance level.

```{r table, echo = FALSE}
kable(crit_table, caption = "Upper critical values of the Mann-Whitney 
                             U distribution")
```

The statistic $U$ counts the pairwise comparisons won by group A.
Determine the rejection region. 

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========
The rejection region is: `r t$solution`

```{r solutionlist, echo = FALSE, results = "asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: mannwhitney3
