---
title: "Central 95% interval of normal distribution"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)

hook(sigma2, sigma^2)

task <- "normal1"
plfile <- file.path("rexams", sprintf("%s.pl", task))
rolog::consult(system.file(plfile, package="mistakes"))

## DATA GENERATION
repeat
{
  mu <- sample(40:160, 1)
  sd_x <- sample(2:8, 1)
  sigma2 <- sd_x^2

  Q <- quote(search(normal1, normal1(mu, sigma2), .S, .R, .P, .E))
  S <- findall(Q, options=list(preproc=as.rolog), env=environment())

  if(problems(S))
    next

  break
}

t <- prepare(task=task, S)
sol <- format_feedback(
  t$correct, t$explanations, t$praise, t$blame, t$extra
)
```

Question
========

A normally distributed random variable $X$ has mean
$\mu = `r mu`$ and variance $\sigma^2 = `r sigma2`$.

Determine the interval, symmetric about the mean, that contains
approximately 95% of its realizations.

```{r questionlist, echo=FALSE, results="asis"}
answerlist(t$alternatives, markup="markdown")
```

Solution
========

The standard deviation is
$\sigma = \sqrt{`r sigma2`} = `r sd_x`$.

The central interval containing approximately 95% of realizations is

$$
[\mu - 1.96\sigma;\ \mu + 1.96\sigma].
$$

The range is calculated by: `r t$solution`

```{r solutionlist, echo=FALSE, results="asis"}
sol <- lapply(sol, FUN=gsub, pattern="\\n", replacement="")
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(t$correct, single=TRUE)`
exname: normal1
