---
title: "Phase II clinical study"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(mistakes)

hook(d, mean(D))
hook(s_d, subscript(s, D))
hook(mu_d, subscript(mu, D))
hook(n, N)
hook(pvalue(.P), .P)
hook(pt1(.X, .DF, .Tail), pt(.X, .DF, .Tail))

dist <- function(Symb, X, Tail)
  return(X)

tail <- function(Tail)
  return(Tail)

pt1 <- function(X, DF, Tail)
{
  if(Tail == "lower")
    return(pt(X, DF, lower.tail=TRUE))

  if(Tail == "upper")
    return(pt(X, DF, lower.tail=FALSE))

  if(Tail == "two.sided")
    return(2 * pt(abs(X), DF, lower.tail=FALSE))

  stop("Tail must bei either upper, lower or two.sided")
}

## DATA GENERATION
repeat
{
  n      <- as.integer(round(runif(1, min=20, max=45)))
  Id     <- 1:n
  T0     <- round(runif(n, min=15, max=40))
  EOT    <- round(T0 + runif(n, min=-10, max=2))
  mu_d   <- round(runif(1, min=2, max=5), 1)

  data   <- data.frame(Id, T0, EOT)
  t0     <- mean(data$T0)
  s_t0   <- sd(data$T0)
  eot    <- mean(data$EOT)
  s_eot  <- sd(data$EOT)
  d      <- mean(data$T0 - data$EOT)
  s_d    <- sd(data$T0 - data$EOT)
  tratio <- (d - mu_d) / (s_d / sqrt(n))
    
  if(abs(tratio) < 0.1)
    next
  if(abs(tratio) > 3.0)
    next
  tails  <- "two-tailed"
    
  alpha  <- 0.05
  break
}

rolog::consult(system.file("rexams/pvalue.pl", package="mistakes"))

Q <- quote(search(pvalue(d, mu_d, s_d, n, alpha), .S, .R, .P, .E))
S <- findall(Q, options=list(preproc=as.rolog), env=.GlobalEnv)

questions <- character(length(S))
solutions <- logical(length(S))
explanations <- character(length(S))

if(length(S) == 0)
  stop("No solutions found.")

for(i in 1:length(S))
{
  Si <- S[[i]]$S
  Ri <- S[[i]]$R
  Pi <- S[[i]]$P
  Ei <- S[[i]]$E

  questions[i] <- Ri
  solutions[i] <- all(expert(Pi))
  e1 <- sprintf("The result matches the following expression: %s\n", mathml(Si))
  e2 <- paste(feedback(Pi), collapse=" ")
  e3 <- paste(feedback(Ei), collapse=" ")
  explanations[i] <- paste(e1, e2, "Extra information:", e3)
}

o <- sample(1:length(S))
questions <- questions[o]
solutions <- solutions[o]
explanations <- explanations[o]
S <- S[o]
```

Question
========
Consider a clinical study on rumination-focused Cognitive Behavioral
Therapy (rfCBT) with `r n` patients. The primary outcome is the score on the
Hamilton Rating Scale for Depression (HRSD, range from best = 0 to worst = 42).
The significance level is set to $\alpha = 5\%$ two-tailed.

````{r, echo=FALSE}
Tab <- rbind(
  Average=c(T0=t0, EOT=eot, `$D$`=d),
  SD=c(T0=s_t0, EOT=s_eot, `$D$`=s_d))
  
knitr::kable(Tab, digits=1, align = c("l", "c", "c"), 
  caption="_Table 1._ HRSD scores.")
````

Does rfCBT lead to a relevant reduction (i.e., more than `r mu_d` units) in mean
HDRS scores between baseline (T0) and End of Treatment (EOT)? Please report
the $p$-value.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(questions, markup="markdown")
```

Solution
========
The $t$-statistic is calculated by: `r mathml(S[[which(solutions)[1]]]$S)`

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(solutions, "True", "False"), explanations, markup = "markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(solutions, single=TRUE)`
exname: p-value
