---
title: "Phase II clinical study"
---

```{r, include=FALSE}
library(exams)
library(mathml)
library(htmltools)
library(mistakes)

hook(d, mean(D))
hook(s_d, subscript(s, D))
hook(mu_d, subscript(mu, D))
hook(n, N)
hook(t0, mean("T0"))
hook(s_t0, subscript(s, "T0"))
hook(eot, mean("EOT"))
hook(s_eot, subscript(s, "EOT"))
hook(s_pool, subscript(s, "pool"))

var_pool <- function(n1, v1, n2, v2)
  frac((n1 - 1L) * v1 + (n2 - 1L) * v2, n1 + n2 - 2L)

hook(var_pool)

## DATA GENERATION
repeat
{
  n      <- as.integer(round(runif(1, min=20, max=45)))
  Id     <- 1:n
  T0     <- round(runif(n, min=15, max=40))
  EOT    <- round(T0 + runif(n, min=-10, max=2))
  mu_d   <- round(runif(1, min=2, max=5), 1)

  data   <- data.frame(Id, T0, EOT)
  t0     <- mean(data$T0)
  s_t0   <- sd(data$T0)
  eot    <- mean(data$EOT)
  s_eot  <- sd(data$EOT)
  d      <- mean(data$T0 - data$EOT)
  s_d    <- sd(data$T0 - data$EOT)
  tratio <- (d - mu_d) / (s_d / sqrt(n))
    
  if(abs(tratio) < 0.1)
    next
  if(abs(tratio) > 3.0)
    next
  tails  <- "two-tailed"
    
  alpha  <- 0.05
  break
}

rolog::consult(system.file("rexams/tratio.pl", package="mistakes"))

Q <- quote(search(tratio, tratio(t0, s_t0, eot, s_eot, d, mu_d, s_d, n), .S, .R, .P, .E))
S <- findall(Q, options=list(preproc=as.rolog), env=environment())

alternatives <- character(length(S))
correct <- logical(length(S))
explanations <- character(length(S))
praise <- list(length(S))
blame <- list(length(S))
extra <- list(length(S))

if(length(S) == 0)
  stop("No solutions found.")

for(i in 1:length(S))
{
  Si <- S[[i]]$S
  Ri <- S[[i]]$R
  Pi <- S[[i]]$P
  Ei <- S[[i]]$E

  alternatives[i] <- sprintf("%.2f", Ri)
  correct[i] <- all(expert(Pi))
  explanations[i] <- sprintf("The result matches the following expression: %s\n", mathml(Si))
  praise[[i]] <- praise("tratio", Pi)
  blame[[i]] <- blame("tratio", Pi)
  extra[[i]] <- feedback("tratio", Ei)
  if(length(extra[[i]]) > 0)
    extra[[i]] <- c("Extra information: ", extra[[i]])
}

# number of MC alternatives, reduce if needed, but make sure the correct
# alternative is in the set
A <- length(S)

# Shuffle
o <- sample(1:A)
alternatives <- alternatives[o]
correct <- correct[o]
explanations <- explanations[o]
praise <- praise[o]
blame <- blame[o]
extra <- extra[o]
S <- S[o]

# Improve formatting
p_correct <- lapply(FUN=tags$p, correct)
h_explanations <- lapply(FUN=HTML, explanations)
p_explanations <- lapply(FUN=tags$p, h_explanations)
h_praise <- lapply(FUN=function(x) lapply(FUN=HTML, x), praise)
p_praise <- lapply(FUN=function(x) tagList(tags$em("Expert"), tags$ul(lapply(FUN=tags$li, x))), h_praise)
h_blame <- lapply(FUN=function(x) lapply(FUN=HTML, x), blame)
p_blame <- lapply(FUN=function(x) tagList(tags$em("Buggy"), tags$ul(lapply(FUN=tags$li, x))), h_blame)
h_extra <- lapply(FUN=function(x) lapply(FUN=HTML, x), extra)
p_extra <- lapply(FUN=function(x) tagList(tags$em("Extra"), tags$ul(lapply(FUN=tags$li, x))), h_extra)

div_sol <- mapply(p_correct, p_explanations, p_praise, p_blame, p_extra,
  FUN=tagList, SIMPLIFY=FALSE)
sol <- lapply(div_sol, FUN=gsub, pattern="\\n", replacement="")
```

Question
========
Consider a clinical study on rumination-focused Cognitive Behavioral
Therapy (rfCBT) with `r n` patients. The primary outcome is the score on the
Hamilton Rating Scale for Depression (HRSD, range from best = 0 to worst = 42).
The significance level is set to $\alpha = 5\%$ two-tailed.

````{r, echo=FALSE}
Tab <- rbind(
  Average=c(T0=t0, EOT=eot, `$D$`=d),
  SD=c(T0=s_t0, EOT=s_eot, `$D$`=s_d))
  
knitr::kable(Tab, digits=1, align = c("l", "c", "c"), 
  caption="_Table 1._ HRSD scores.")
````

Does rfCBT lead to a relevant reduction (i.e., more than `r mu_d` units) in mean
HDRS scores between baseline (T0) and End of Treatment (EOT)? Please report
the $t$-ratio.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(alternatives, markup="markdown")
```

Solution
========
The $t$-statistic is calculated by: `r mathml(S[[which(correct)[1]]]$S)`

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup="markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(correct, single=TRUE)`
exname: t-ratio
